ManuscriptPURFits

### 2024-02-15 Code/ManuscriptPURFits.Rmd
Combined PURfit for each strain into 1 plot

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
#library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(AICcmodavg)
# library(RColorBrewer)
# library(grid)
# library(bookdown)
# library(glue)
# library(egg)
# library(ggspectra)
# library(photobiologyWavebands)
# library(photobiology)
#library(ggpubr)
#library(ggh4x)
#library(cowplot)
#library(jmv)
# library(pgirmess) # for the post hoc kruskalalmc test
#library(rcompanion) # for Scheirer-Ray-Hare non-parametric 2 way test, derived from Kruskal-Wallis
# library(FSA) # for Dunn test
#library(dunn.test)
# library(rstatix)
library(minpack.lm)

@@

MED4PURFITPlot <- AllFitsCombined |>
    filter(Strain == "MED4") |>
  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
  ggplot() +
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
  labs(title = "MED4", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "top") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )
MED4PURFITPlot

SS120PURFITPlot <- AllFitsCombined |>
    filter(Strain == "SS120") |>
  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
  ggplot() +
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
     labs(title = "SS120", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "top") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )
   SS120PURFITPlot

MIT9313PURFITPlot <- AllFitsCombined |>
   filter(Strain == "MIT9313") |>
  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
  ggplot() +
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "twodash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
  labs(title = "MIT9313", y = "Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")", x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
  scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
  scale_linetype_manual(values = c("solid","twodash","dashed", "dotted", "aa"), labels = c("Pooled","16 hr", "12 hr", "8 hr", "4 hr")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, Photoperiod = label_value, PhotoperiodLabel_title = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title = element_text(size = 30, color = "black"),
        axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "top") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )
MIT9313PURFITPlot

@@

ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".tiff",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".tiff",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".tiff",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
#library(stringr)
library(broom)
library(knitr)
library(zoo)
#library(AICcmodavg)
# library(RColorBrewer)
library(grid)
library(gridExtra)
# library(bookdown)
# library(glue)
# library(egg)
# library(ggspectra)
# library(photobiologyWavebands)
# library(photobiology)
#library(ggpubr)
#library(ggh4x)
library(cowplot)
#library(jmv)
# library(pgirmess) # for the post hoc kruskalalmc test
#library(rcompanion) # for Scheirer-Ray-Hare non-parametric 2 way test, derived from Kruskal-Wallis
# library(FSA) # for Dunn test
#library(dunn.test)
# library(rstatix)
library(minpack.lm)

@@

MED4PURFITPlot <- AllFitsCombined |>
    filter(Strain == "MED4") |>
  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
  ggplot() +
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MED4")) + 
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(O2_uM != 2.5, Strain == "MED4")) +
 geom_text(aes(x = 1000, y = 0.9, label= "A"), data = . %>% filter(O2_uM == 250, Strain == "MED4"), size = 20, hjust = 0.3, vjust = 0) +
  scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title.y = element_blank(),
        axis.title.x.bottom = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "top") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )
MED4PURFITPlot

SS120PURFITPlot <- AllFitsCombined |>
    filter(Strain == "SS120") |>
  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
  ggplot() +
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "SS120")) + 
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM == 250, Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(Strain == "SS120")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "SS120")) +
 geom_text(aes(x = 1000, y = 0.9, label= "B"), data = . %>% filter(O2_uM == 250, Strain == "SS120"), size = 20, hjust = 0.3, vjust = 0) +
  scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  # coord_cartesian(ylim = c (0, 0.07)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
  scale_linetype_manual(values = c("twodash","dashed", "dotted", "aa"), labels = c("16 hr", "12 hr", "8 hr", "4 hr")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
 # guides(linetype = guide_legend(nrow = 4),
 #        fill = "none",
 #        colour = guide_legend(nrow = 4)) +
 # guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
        axis.title.y = element_blank(),
        axis.title.x.bottom = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "none") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )
   SS120PURFITPlot

MIT9313PURFITPlot <- AllFitsCombined |>
   filter(Strain == "MIT9313") |>
  unnest(cols = c(Data_all), names_sep = "_", keep_empty = TRUE) |>
  mutate(PhotoperiodLabel_title = "Photoperiod (h)",
         OxygenLabel = "Oxygen Concentration (µM)",
         Photoperiod = factor(Data_all_Photoperiod, levels = c("16", "12", "8", "4" )),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5)),
         WL = factor(Data_all_WL, levels = c("WW", 660, 450))) %>%
  ggplot() +
  geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_ReplicateMean_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 6, alpha = 1.0) +
    geom_point(aes(x = Data_all_PURPhotonDose_day, y = Data_all_deltaOD_Lmu_corr_day, shape = as.factor(Photoperiod), color = as.factor(WL), fill = as.factor(WL)), size = 2, alpha = 0.8) +
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 2, linetype = "solid", data = . %>% unnest(Predict_pooled) %>%  filter(Strain == "MIT9313")) + 
  geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "twodash", data = . %>% unnest(Predict_16) %>%  filter(O2_uM == 2.5, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dashed", data = . %>% unnest(Predict_12) %>%  filter(O2_uM != 2.5, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "dotted", data = . %>% unnest(Predict_8) %>%  filter(O2_uM == 25, Strain == "MIT9313")) +
   geom_line(aes(x = PURPhotonDose_day, y = .fitted), size = 0.5, linetype = "aa", data = . %>% unnest(Predict_4) %>%  filter(Strain == "MIT9313")) +
  labs(x = "PUR (µmol photons" ~m^-2 ~d^-1~")") +
 geom_text(aes(x = 1000, y = 0.9, label= "C"), data = . %>% filter(O2_uM == 250, Strain == "MIT9313"), size = 20, hjust = 0.3, vjust = 0) +
  scale_x_continuous(label=scientific_10) +
   scale_y_continuous(breaks = c(0,0.2, 0.4, 0.6, 0.8, 1.0), limits = c (0, 1.05)) +
  scale_colour_manual(values = MCMIXColours, labels = c("White LED", 660, 450)) +
  scale_linetype_manual(values = c("solid","twodash","dashed", "dotted", "aa"), labels = c("Pooled","16 hr", "12 hr", "8 hr", "4 hr")) +
   scale_shape_manual(values = PhotoperiodShapes)  +
  ggh4x::facet_nested(rows = vars(OxygenLabel, O2_uM), 
                    labeller = labeller(Strain = label_both, WL = label_both, O2_uM = label_value, OxygenLabel = label_value)) +
 guides(linetype = guide_legend(nrow = 4),
        fill = "none",
        colour = guide_legend(nrow = 4)) +
 guides(shape = guide_legend(nrow = 4)) +
  theme_bw() +
   theme( strip.text = element_text(size = 30),
          axis.title.y = element_blank(),
          axis.title.x = element_text(size = 30, color = "black"),
          axis.text.x = element_text(size = 20, color = "black", angle = 45, hjust = 1.0),
          axis.text.y = element_text(size = 20, color = "black", angle = 0, hjust = 1.0),
        strip.background=element_rect(color="grey87", fill = "grey82"),
        # strip.background=element_rect(fill = "white"),
        legend.key.size = unit(1, 'cm'), #change legend key size
        legend.key.height = unit(1, 'cm'), #change legend key height
        legend.key.width = unit(0.5, 'cm'), #change legend key width
        legend.title =  element_text(size = 30),  #change legend title font size
        legend.text = element_text(size = 30),   #change legend text font size
        legend.position = "none") +
  labs( shape = "Photoperiod (h)",
        color = "Growth Waveband (nm)",
       linetype = "Photoperiod (h) "
      )
MIT9313PURFITPlot

# Combine the 3 strains into 1 plot 
```{r combine plots}

AllStrainPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)

#create common x and y labels
y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
                   gp = gpar(col="black", fontsize = 20), rot = 90)

#add to plot
AllStrainPurFitsPlots <- grid.arrange(arrangeGrob(AllStrainPurFitsPlots, left = y.grob))

@@

ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

# ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".png",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".png",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".png",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("MED4PURFITPlot",".tiff",sep = "")), plot = MED4PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("SS120PURFITPlot",".tiff",sep = "")), plot = SS120PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
# 
# ggsave(file = file.path(PlotsOut, paste("MIT9313PURFITPlot",".tiff",sep = "")), plot = MIT9313PURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
